Modular Inverse Reinforcement Learning on Human Motion

### 2015-02-23 content.tex
update content

Figure~\ref{fig:avatar} shows the experimental domain. The
human subject was immersed in a virtual reality domain by wearing a binocular head-mounted display.
The subject's eye, head, and body motion were tracked as he/she walked through a
virtual environment that was designed to match the dimensions of a standard indoor
environment. The subject was asked to follow the path, avoid the obstacles (red
cubes), and collect the targets (blue spheres) by intercepting them. In
different conditions they were asked to give different importance to particular
sub-tasks, with sub-tasks being either relevant or irrelevant. Subjects were
given auditory feedback when running into obstacles, and when intercepting
targets, depending on their importance in the current condition. Thus this
domain can be modeled by three modules, 1) following the path, 2) collecting targets, 3)
avoiding obstacles.  This general paradigm has been used to evaluate modular
reinforcement learning \cite{rothkopf2013modular} and understand human behavior
\cite{Tong2014}.

@@

%COMMENT: Shun, the modular formulation started with Sprague et al ACM Trans. of Applied Perception 4(2), 1 , 2007 and this should be referenced.
%The Parr and Koller paper is about factored MDPs which is diofferent than modular MDPs. The Thomas and Barto is a much more recent paper
%that learns motor MDPs in a very restructed domain.
In the literature, modular formation is proposed for understanding human
visuomotor behavior \cite{sprague2007modeling}. A combination of various basic
modules can generate complex behavior to match human behavior.
Following \cite{sprague2007modeling, rothkopf2013modular}, we consider how the
modules can be combined. Here we assume that the global Q function is a weighted
sum of all $Q_i$, where $Q_i$ is the Q function for i-th module.
$$Q(s, a) = \sum_i w_i Q_i (s_i, a)$$
where $w_i$ is the weight of the i-th sub-MDP. $w_i \geq 0, \sum_i w_i = 1$.
$s_i$ denotes the decomposition of $s$ in the i-th module.

>>>>

Figure~\ref{fig:avatar} shows the experimental domain. The
human subject was immersed in a virtual reality domain by wearing a binocular head-mounted display.
The subject's eye, head, and body motion were tracked as he/she walked through a
virtual environment that was designed to match the dimensions of a standard indoor
environment. The subject was asked to follow the path, avoid the obstacles (red
cubes), and collect the targets (blue spheres) by intercepting them. In
different conditions they were asked to give different importance to particular
sub-tasks, with sub-tasks being either relevant or irrelevant. Subjects were
given auditory feedback when running into obstacles, and when intercepting
targets, depending on their importance in the current condition. Thus this
domain can be modeled by three modules, 1) following the path, 2) collecting targets, 3)
avoiding obstacles.  This general paradigm has been used to evaluate modular
reinforcement learning \cite{Rothkopf12Infer, rothkopf2013modular} and understand human behavior
\cite{Tong2014}.

@@

%COMMENT: Shun, the modular formulation started with Sprague et al ACM Trans. of Applied Perception 4(2), 1 , 2007 and this should be referenced.
%The Parr and Koller paper is about factored MDPs which is diofferent than modular MDPs. The Thomas and Barto is a much more recent paper
%that learns motor MDPs in a very restructed domain.
In the literature, modular formation is proposed for understanding human
visuomotor behavior \cite{sprague2007modeling}. A combination of various basic
modules can generate complex behavior to match human behavior.  The combination
can be either of Q functions of modules \cite{rothkopf2013modular} or of rewards
of modules \cite{Rothkopf12Infer}.
Following \cite{sprague2007modeling, rothkopf2013modular}, we consider how the
modules can be combined. Here we assume that the global Q function is a weighted
sum of all $Q_i$, where $Q_i$ is the Q function for i-th module.
$$Q(s, a) = \sum_i w_i Q_i (s_i, a)$$
where $w_i$ is the weight of the i-th sub-MDP. $w_i \geq 0, \sum_i w_i = 1$.
$s_i$ denotes the decomposition of $s$ in the i-th module.
